---
output: 
  github_document:
    toc: true
    toc_depth: 2
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}

ratio <- (1 + sqrt(5)) / 2

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  screenshot.opts = list(
      vwidth = floor(800 * ratio),
      vheight = 800
  ))
```

# Plotscaper

<!-- badges: start -->
<!-- badges: end -->

Plotscaper is a package for making linked interactive figures for data exploration. 

## Quick start

To get started, install `plotscaper` from [GitHub](https://github.com/) with:

```{r}
#| eval: false
devtools::install_github("bartonicek/plotscape/packages/plotscaper")
```

Next, open up RStudio and run the following code:

```{r}
#| fig-align: center
library(plotscaper)

layout <- matrix(c(
  1, 1, 2, 3,
  1, 1, 4, 5,
  6, 7, 7, 7
), ncol = 4, byrow = TRUE)

set_scene(sacramento) |>
  add_scatterplot(c("longitude", "latitude")) |>
  add_barplot("city") |>
  add_histogram(c("sqft")) |>
  add_fluctplot(c("beds", "baths")) |>
  add_histogram2d(c("sqft", "price")) |>
  add_notes() |>
  add_parcoords(names(sacramento)) |>
  set_layout(layout)
```

In your viewer, you should now see something like the image above, however, your version should be fully interactive (the snapshot above is static is because `README.md` does not allow JavaScript, unfortunately).

Try moving your mouse somewhere over the big scatterplot on the top left, clicking and dragging to select some points. You should see the corresponding cases highlight across all the other plots! 

There are many other ways interacting with the figure. Click on the question mark button in the top right of the figure to see a list of the available options.

## Anatomy of a `plotscaper` figure

There are quite a few things happening in the code above. Let's break it down piece by piece.

First, whenever we want to create a `plotscaper` figure, we need to set up a scene. A scene is a kind of context into which all plots get placed. 

To set up a scene, run:

```{r}
#| eval: false
set_scene(data = sacramento)
```

where `data` is a `data.frame` object. Here we're using the Sacramento housing dataset from the `caret` package.

On its own, however, a scene doesn't do anything. To create an interactive figure, we need to populate it with plots. That's what the various `add_*` functions are for:

```{r}
set_scene(sacramento) |>
  add_scatterplot(c("longitude", "latitude")) |>
  add_barplot("city")
```

As you can see above, this creates a simple interactive figure with a scatterplot and a barplot. Not much more to it. We identify what variables we want to plot by a simple character vector of their names.   
